\backmatter
\begin{ack}

In 2004, I came to Huazhong University of Science and Technology as an undergraduate student. Now, I am over 30. The completion of the doctoral dissertation indicates that my student life here is coming to an end. Although I had discouraged days in the unforgivable life, when I staggering to leave the land that accomplished my grown up years, I am grateful for all the hardships and joys I have experienced.
The full harvest of both academic and life will change my life journey.

You miss a place because you miss the people there. Special thanks for professor Huang Shuhong, I learned a lot during those years being with you. I have been deeply infected by your academic attitude, working spirit and personal charisma. Your unique academic insight and acute academic ideas always inspired me. 

After he past away, I dreamed about my tutor several times, especially when I was depressed. Recalling your teachings and encouragements, I always re-establish my confidence to overcome the difficulties. Face to face learning is a collection of my memory. Professor’s firm academic enthusiasm will continue to guide me.

Many thanks to the teachers who provide guidances and helps in these years. I offer my thanks to Professor Gao Wei, his elegant temperament and broad mind set up a good example for personal relationship and learning approaches.
I would like to thank Associate Professor Zhang Yanping for urging me to study and write from time to time, paying close attention to the progress of the papers, and giving many timely wit directions.
Special thanks for professor Inmaculada Arauzo, I am lucky enough to follow you to University of Zaragoza to open a new academic perspective. Your easy-going temper, warm attitude make my life in Spain warm and fulfilling. Your rigorous spirit and deep insight influenced me a lot. I also show my thanks to Teacher He and Yang, they concerned about me and helped me. The completion of my study comes with the generous guidance and encouragement of the teachers.

In the academic team, I was fortunate to meet Lv Fangming, Wang Jizhou, Zou Chongzhe. We learned a lot from each other and created precious memories. In the days with Rahul and Daniel, I improved my English communication ability and writing skills.

Finally, I thank my family for their understanding and support. I am grateful to my parents for their hard work and strong support. Thank you, my wife, after our daughter Tongtong was born, you carried the burden of taking care of this little life. Thank you, Tongtong, your cleverness and cuteness are the flavors of my life and they always make me full of power.

Time to say goodbye. This will be a new starting point for my life. I will stay true to my mission, follow my heart, and manage a new life with gratitude and expectations.
\\
\\


\begin{flushright}
	Zhang Cheng
	
	December 14, 2017
\end{flushright}

\end{ack}
